Tensor anisotropy as a tracer of cosmic voids

### 2015-06-20 first_cosmic_voids.tex
latex first submitted version

% To highlight comments 
\definecolor{red}{rgb}{1,0.0,0.0}
\newcommand{\red}{\color{red}}
\definecolor{darkgreen}{rgb}{0.0,0.5,0.0}
\newcommand{\SRK}[1]{\textcolor{darkgreen}{\bf SRK: \textit{#1}}}
\newcommand{\SRKED}[1]{\textcolor{darkgreen}{\bf #1}}
\newcommand{\before}[1]{\textcolor{red}{ #1}}
\newcommand{\after}[1]{\textcolor{darkgreen}{ #1}}

@@

Here we introduce a new algorithm to define voids over the continous
matter density or velocity distribution defined on a fixed and
homogeneous spatial grid.
The algorithm uses the results from two tensorial schemes used to
classify the cosmic web.
The first (the T-Web) is based on the Hessian of the gravitational potential or
tidal tensor \citep{Hahn07, Forero09}. 
The second (the V-web) is based on the velocity shear tensor
\citep{Hoffman12}. 
Our procedure allows for a description of a void internal structure
beyond a simple definition of a void as an underdense region in the
large-scale matter distribution. 
The tidal and the shear tensors
encode more information than the density/velocity fields as they trace
the collapsing or expanding nature of the matter field, which defines
the dynamics of the Cosmic Web.

The tracer that we use to define the voids is the fractional
anisotropy (FA) computed from the set of eigenvalues of the tensor
under consideration. 
The FA was initially introduced by \citet{Basser95} to quantify the
anisotropy degree of the diffusivity of water molecules through
cerebral tissue in nuclear magnetic resonance imaging, thereby allowing to 
detect structures that restrict the otherwise isotropic Brownian movement 
of water molecules. Taking into account that this process is identical to 
the velocity shear in the large-scale matter distribution, 
\citet{Libeskind13} introduced the concept of the FA in the context of 
Cosmic Web classification schemes.

%!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!

@@

%.........................................................................
%FIGURE 1: FA and vissual impression
\begin{figure*}
  \includegraphics[trim = 16mm 8mm 5mm 12mm, clip, keepaspectratio=true,
  width=0.73\textheight]{cosmicweb_FA_Tweb.pdf}
  \includegraphics[trim = 16mm 8mm 5mm 12mm, clip, keepaspectratio=true,
  width=0.73\textheight]{cosmicweb_FA_Vweb.pdf}
  \caption{Different fields in a slice of
    $1\hMpc$ width in the Bolshoi simulation. Top/bottom panels correspond
    to the T-Web/V-Web.      
    Fractional Anisotropy field (left); cosmic web classification
    (middle) for a given value of the threhold eigenvalue
    $\lambda_{\rm th}$ where voids are white, sheets are light gray,
    filaments are dark gray and knots are black; individual voids (right) found by 
    the a watershed algorithm on the Fractional Anisotropy field. Colours
    in the right panel correspond with the effective radius of each void. }
  \label{fig:FA_field}
\end{figure*}
%.........................................................................

@@

Usually, the threshold $\lambda_{th}$ is a free parameter that is
tuned to reproduce the visual appearence of the comic web. 
However, in this paper this threshold does not play any role in our
computations.
In Figure \ref{fig:L1_correlations} we offer a threshold estimate
(from the FA=$0.95$ as a function of $\lambda_1$, this choice is
explained in the next section) only as a guide to readers familiar
with its meaning.

%-------------------------------------------------------------------------
%FIGURE 2: Distributions of FA and density regarding the Lambda_1 eigenvalue
\begin{figure*}
\centering
  \includegraphics[trim = 1mm 0mm 5mm 10mm, keepaspectratio=true,
  width=0.33\textwidth]{FA_L1.pdf}  
  \includegraphics[trim = 1mm 0mm 5mm 10mm, keepaspectratio=true,
  width=0.33\textwidth]{delta_L1.pdf}
  \includegraphics[trim = 1mm 0mm 5mm 10mm, keepaspectratio=true,
  width=0.33\textwidth]{FA_delta.pdf}
  \captionof{figure}{
    Fractional Anisotropy  as a function of
    the overdensity (left) and the eigenvalue $\lambda_1$ (middle), and
    density contrast (right) as a function of the
    eigenvalue $\lambda_1$ for each web scheme (T-Web,  continous
    lines. V-Web, dashed lines).     
    Fractional Anisotropy  as a function of $\lambda_1$ (left),
    overdensity as a function of $\lambda_1$ (middle) and Fractional
    Anisotropy as a function of the overdensity (right).
    Thick central lines are the median
    and filled regions include $50\%$ of the cells in each bin. 
    The left panel shows the tigth correlation between FA and
    $\lambda_1$ in voids.
    In the middle and right panel we show the equivalent eigenvalue
    threshold for the T-Web and V-web corresponding to FA=$0.95$. 
    The right panel confirms that underdense regions can be
    identified with Fractional Anisotropy values less than $0.95$.
    For this reason we define voids to be composed by cells with
    Fractional Anisotropy equal or less than this value.
    The threshold $\lambda_{\rm th}$ on the eigenvalues does not
    influence our results. 
    We show it as a guide to readers familiar with the
    order of magnitude expectation for this quantity.}
  \label{fig:L1_correlations}

@@

%-------------------------------------------------------------------------
%FIGURE 3: Histograms for each environment regarding the FA value
\begin{figure}
\centering
  \includegraphics[trim = 1mm 0mm 5mm 10mm, clip, keepaspectratio=true,
  width=0.35\textheight]{FA_environment.pdf}
   \captionof{figure}{\small Volume of each environment per FA
   ($dV_i/dFA,\ \ i=v,s,f,k$) normalized by the total volume per FA
   ($dV/dFA$). 
  Top/bottom corresponds to the T-Web/V-Web. For a given value of the FA, 
  each line represents the volume contribution of the respective 
  environment to the total volume with the same FA value. Above FA=0.95,
  only sheets and filaments contribute to all the volume of the simulation
  within that range of FA.}
  \label{fig:FA_environment}
\end{figure}
%.........................................................................

@@

% CORRECTION !!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!

The fractional anisotropy (FA), as developed by \citet{Basser95}, 
was conceived to quantify the anisotropy of the diffusivity of water
molecules through cerebral tissue in nuclear magnetic resonance imaging. 
In this manner, barriers such as microtubules and cell membranes, that 
restrict the otherwise isotropic Brownian motion of water molecules, can 
be detected. In a cosmological context, the problem of finding structures 
is very similar, where filaments and sheets restrict the otherwise 
isotropic collapsing/expanding dynamics of the matter. Taking this into 
account, we present here the FA, much in the same way as \citet{Libeskind13}, 
to use it as a tracer of cosmic voids.

%!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!

@@

In the left and middle panels of Fig. \ref{fig:FA_field} we show the
FA field and web classification for both  web schemes over a slice of
an N-body simulation (described in Section \ref{sec:simulations}). 
Comparing these two panels we see that voids and knots (white
and black in the middle panel of Fig. 1) display low FA values at
their  centres, becoming gradually more anisotropic at outer regions.  
On the other hand the filamentary structure (grey in the middle panel
of Fig. 1) is traced by middle to high FA values.  
This characteristic is the  key to use the FA as a tracer of cosmic
voids.

@@

Voids are regions where $\lambda_3\leq\lambda_2\leq
\lambda_1\leq\lambda_{\rm th}$. 
This implies that a void is completely fixed by the relative strength
of the $\lambda_1$ eigenvalue with respect to the threshold.   
As we increase/decrease the threshold value $\lambda_{\rm th}$, voids
increase/decrease progressively through contours of
increasing/decreasing $\lambda_1$.  
Voids are thus characterized by low values of both FA and
$\lambda_1$.

In Fig. \ref{fig:L1_correlations}  we show that the these two values
are correlated. 
The left panel shows the correlation between the FA and $\lambda_1$
and the middle panel between the overdensity $\delta$ and $\lambda_1$.
The right panel shows the correlation between $\delta$ and the
FA. 
This shows that the  density has a larger scatter at fixed
$\lambda_1$ than the FA, yet large and  small values of the density
remain still associated to low values of the FA.

At this point, the eigenvalue $\lambda_1$ and the FA appear to be
equally potential candidates for tracing cosmic voids, however, the 
eigenvalue $\lambda_1$ presents, along with the overdensity, an undesirable 
feature for a void tracer. 
As we move out from inner parts of voids to outer parts, $\lambda_1$
and $\delta$ increase monotonically making unclear where to set the
void boudary, while for low density regions ($\delta<1$) the FA traces
the boundary where anisotropic collapse regions begin to 
dominate.
According to Fig. \ref{fig:FA_environment} these anisotropic areas are
mainly associated to sheets and, to a lesser extent, filaments.

From Figs. \ref{fig:FA_field} and \ref{fig:L1_correlations} we
conclude that the FA is a good tracer of voids as it is almost perfectly
correlated with low values of $\lambda_1$. 
We propose that voids should be composed completely by regions of
FA$<0.95$.
If we increase the values of $\lambda_1$ from its minimum until it
we reach FA$=0.95$ in \ref{fig:L1_correlations} we find that this
correspond to critical values of $\lambda_{1}^T = 0.265$ and
$\lambda_{1}^V = 0.175$ for the T-Web and V-Web, respectively.
This means that setting $\lambda_{th}$ to either
$\lambda_{1}^T$/$\lambda_{1}^{V}$ automatically produces voids with
all the cells FA$<0.95$.   
The middle panels in Fig. \ref{fig:FA_field} show the web
classification for this choice of $\lambda_{th}$, demonstrating that
this FA level is a reasonable choice to define voids.

@@

However, there are two main differences in our approach with respect to other
watershed implementations.
First, the watershed technique commonly uses the density field
instead of the FA field as we do here
\citep{Platen07,Neyrinck08}.   
Second, we estimate all relevant quantities on a Cartesian mesh of
fixed cell size, while other works use an adaptive Delaunay tessellation
\citep{Schaap00}.
Nevertheless, in our case the average number of particles per cell
  is large enough ($512$ particles/cell) ensuring that the lowest
  density regions are sampled with at least $\sim 10$ particles
  ($\delta \sim-0.98$), which seems to avoid spurious results from a
  noisy density field sampling.

The watershed algorithm also needs a threshold value to reduce
spurious features and prevent void hierarchization.  
If the density field is used, a typical threshold is
$\delta = -0.8$ \citep{Platen07},  which means that, given two neighbouring 
voids, if the mean value of the density across their common boundary is 
below that threshold, the two voids are merged.
In our case we have to find a corresponding FA value
to define this threshold.

In the right panel of Fig. \ref{fig:L1_correlations} we see how 
the FA correlates with the matter overdensity. 
A value of $\delta=-0.8$ corresponds to a value of FA$\sim 0.65$
regardless of the web-finding scheme. 
This is the value we choose to remove ridges between two watershed
voids. 
The right column in Fig. \ref{fig:FA_field} shows all the individual
voids that have been identified using the watershed algorithm on the
FA field.

%.........................................................................
%FIGURE 4: volume functions
\begin{figure*}
\centering

@@

  \captionof{figure}{\small Left panel, void size distribution. Right
    panel, fraction of overcompensated/subcompensated ($C>1/C<1$)voids as a
    function of the effective radius. The continous (dashed)
    curves correspond to the T-Web (V-Web).
    The abundance for small ($\reff <2.0\hMpc$) overcompensated voids
    shoots up in the V-Web scheme.
    We provide in the body of the paper two reasons for this behaviour.}
  \label{fig:volume_function}

@@

We limit our results to voids with effective radius larger than the
smoothing length of the density field, i.e. $\sim 1$\hMpc.  
For smaller interpolation/smoothing scales the shot noise in
  the low density regions starts to be noticeable.
With that choice we find a void volume filling fraction $54.88\%$ and
$47.06\%$ for the FA-Vweb and the FA-Tweb, respectively.  
For larger smoothing scales ($>5\hMpc$) the density and shear fields
  tend to be Gaussian and therefore follow closely the analytical
  environment abundance predictions for Gaussian random fields
  \citep{Forero09,Alonso2015}.  
In this paper we limit ourselves to a smoothing scale $\sim 1$ \hMpc.

@@

Comparing the abundance of large voids in the two web schemes, we find
that the largest voids in the V-Web have $\reff \sim 10$\hMpc,
while the T-Web scheme includes voids as large as $\reff \sim 15$\hMpc. 
This suggests that large voids in the T-Web scheme have a velocity
structure that splits them in the V-Web. 
This increased granularity in the velocity structure of voids is
evident in the left and right panels of Fig. \ref{fig:FA_field}.

%.........................................................................
%FIGURE 5: Density profile of voids for each defined scheme
\begin{figure*}
\centering
  \includegraphics[trim = 2mm 2mm 5mm 0mm, clip, keepaspectratio=true,
  width=0.35\textheight]{voids_density_TwebFAG0.pdf}
  \includegraphics[trim = 2mm 2mm 5mm 0mm, clip, keepaspectratio=true,
  width=0.35\textheight]{voids_density_TwebFAG1.pdf}

@@

We find that voids are distributed in two different families
differentiated by the 
presence/absence of an overdense matter ridge in their density
profiles. 
To discriminate each void in one of the families we use the
compensation  index $C$
It is defined as the mass of a void enclosed in a spherical volume of
radius $R$ and normalized by the mass of the same volume assuming
it is filled by matter with the mean background density.

\eq{compensation}
{C= \frac{M_v}{\overline{M}} = \frac{3}{2R^{3}} \int_0^{R} [\delta(r) + 1] r^2 dr}

We choose an integration radius of $R=4\reff$, that is large enough to 
enclose the compensation ridge for a typical void in case there is one. 
This leads us to voids with $C>1$ having more mass than expected, 
constituting the family of overcompensated voids. 
These voids generally  exhibit a compensation ridge associated to
dense nearby structures. 
In the same fashion, voids with $C<1$ constitute the family
of  subcompensated voids.

In Fig. \ref{fig:density_profile} we show the density and velocity profiles
of voids splitted in these two families. 
In the left column it becomes clear the difference between sub- and
overcompensated voids. 
Table \ref{tab:number_voids} lists the number of voids in 
each effective radius bin for the two web finding methods.

%.........................................................................
\begin{table}[!htbp]
\centering
\begin{tabular}{c | c c | c c}
\toprule
\multicolumn{1}{c}{}&  \multicolumn{2}{c}{\textbf{Tweb}} & \multicolumn{2}{c}{\textbf{Vweb}}\\
%\midrule
\textbf{${\bf \reff }$[\hMpc]}   & $\bf{C<1}$   & $\bf{C>1}$    & $\bf{C<1}$   & $\bf{C>1}$\\ \hline
%\midrule
$<2.0$        &  997 & 495   & 13480  & 711\\
$2.0-3.2$     &  791 & 471   & 2581   & 583\\
$3.2-4.4$     &  941 & 469   & 2168   & 656\\
$4.4-5.6$     &  869 & 467   & 1934   & 724\\
$5.6-6.8$     &  769 & 395   & 1287   & 584\\
$6.8-8.3$     &  665 & 362   & 700    & 315\\
$8.3-12.0$    &  587 & 333   & 123    & 61\\
$>12.0$       &  29  & 23    & 0      & 0\\ \hline
\textbf{total}& 5648 & 3015  & 22273  & 3634\\
\bottomrule
\end{tabular}
\caption{Number of voids for each bin of effective radius and for 
subcompensanted and overcompansated samples.}
\label{tab:number_voids}
\end{table}
%.........................................................................

@@

The first interesting result is the overdensity value at the void's
center.
We find that larger voids have a lower overdensity value.
The largest voids ($8.3-12\ \hMpc$) have an underdensity
$\delta \sim-0.95$ while smaller voids  ($2-3.2\ \hMpc$) fall around $\delta\sim 
-0.8$ at their centers.
This holds for both web schemes. 
These values are consistent with most of the void finding schemes
based on smooth and continuous fields from simulation or
reconstruction procedures on surveys \citep{Plionis02, Colberg05,
  Shandarin06,  Platen07, Neyrinck08, MunozCuartas11, Ceccarelli13,
  Paz13, Neyrinck13, Ricciardelli2013}, unlike geometrical approaches based 
on point distributions, where central density values are generally higher
\citep{Colberg08}.

A second feature about these profiles is their steepnes at inner
regions.  
In subcompensated voids, larger voids are steeper.
Smaller voids exhibit moderate slopes, reaching the mean density at
larger radii than larger voids.
This suggests that small subcompensated voids are embedded into low
density structures, while large subcompensated voids are surrounded
by dense structures, reaching the mean density at lower effective
radii than smaller voids. 
In the overcompensated case larger voids reach first  both the
compensation ridge and then the mean density value.

@@

All the previous results hold for both finding schemes.
This suggests an universal behaviour for the radial density profile in
two families of subcompensated and overcompensanted voids. 
This goes in the same direction of recent results about the internal
\citep{Colberg05,  Ricciardelli2013} and external structure of voids
\citep{Lavaux12, Ceccarelli13, Paz13, Hamaus14}. 
Indeed, our results extend the findings of \cite{Hamaus14} into the
range of voids with size $\reff <10$\hMpc.

@@

We find that subcompensated voids have outflowing velocity profiles
all the way up to the radius where the average radial
density reaches zero.
In voids with sizes $\reff <8\hMpc$ the outflow is always
positive, consistent with the fact that their density profiles do not
reach the level $\delta=0$ in the range of explored radii.
This behaviour indicates that matter is being pulled out of the void
into external higher density features.

@@

Fig. \ref{fig:FA_profile} shows the results for the FA profiles.
We find that the FA clearly magnifies the difference between the
internal profile $r/\reff <1$ and the external profile $r/\reff >1$. 
Subcompensanted voids in the T-Web reach an asymptotic background
value of F=$0.8$ almost right at $r/\reff =2$. 
For the V-Web the results are similar, albeit with a slower trend with
the effective radius. 
Overcompensated voids reach a maximum FA at the same effective radiuus
$r/\reff =1$ and decline to reach an asymptotic value of FA=$0.85$
at larger radii.

@@

The difference between the radius where the density ridge is reached 
($r/\reff =3$) and the radius of the FA maxima ($r/\reff =1$, most
manifest in the T-Web voids) justifies in a more quantiative way the
qualitative argument we present in sub-section \ref{subsec:watershed}
to define void boundaries in our method.  
Namely that as we increase the void boundary moving away from the
center, we reach first middle density walls, before reaching high
density structures associated with high anisotropy.  
This implies that voids defined with the FA never present positive
overdensities, making the FA maximum a reasonable boundary for voids
compared to the traditional definition that puts the boundary at the
densityridge.

@@

A second step in the void characterization 
is the separation into subcompensated and overcompensated samples. 
In the T-Web $35\%$ of the voids are overcompensated and $65\%$
subcompensated, meaning that they are located in denser regions with
a clear delimiting ridge.   
For the V-web the subcompensated fraction rises to $85\%$ as the
void size decreases, supporting the picture of smaller spurious voids
located in medium density matter sheets.

Finally we proceed with a more detailed void characterization
through the radially averaged profiles of density, radial velocity and
fractional anisotropy. 
In this case we study separately the subcompensated and
overcompensated voids, split this time in samples with different
effective radii.

For the density the most interesting feature is that the  profile has
a similar shape for all the different void sizes once the radial
coordinate is expressed in units of the effective radius.  
In these profiles it is evident the presence of an overdense ridge
around $2<r/\reff <3$ for the overcompensated voids.
Subcompensated voids do not show such a ridge keeping its density
lower than the average value up to $r/\reff \sim 8$.

>>>>

% To highlight comments 
\definecolor{red}{rgb}{1,0.0,0.0}
\newcommand{\red}{\color{red}}
\definecolor{darkgreen}{rgb}{0.0,0.5,0.0}
\newcommand{\SRK}[1]{\textcolor{darkgreen}{\bf SRK: \textit{#1}}}
\newcommand{\SRKED}[1]{\textcolor{darkgreen}{\bf #1}}

@@

Here we introduce a new algorithm to define voids over the continous
matter density or velocity distribution defined on a fixed and
homogeneous spatial grid.
The algorithm uses the results from two tensorial schemes used to
classify the cosmic web.
The first (the T-Web) is based on the Hessian of the gravitational potential or
tidal tensor \citep{Hahn07, Forero09}. 
The second (the V-web) is based on the velocity shear tensor
\citep{Hoffman12}. 
Our procedure allows for a description of the internal structure
of voids that goes beyond a simple definition of a void as an
underdense region in the large-scale matter distribution.
The tidal and the shear tensors encode more information than the
density/velocity fields as they trace the collapsing or expanding
nature of the matter field, which defines the dynamics of the Cosmic
Web.

The tracer that we use to define the voids is the fractional
anisotropy (FA) computed from the set of eigenvalues of the tensor
under consideration. 
The FA was initially introduced by \citet{Basser95} to quantify the
anisotropy degree of the diffusivity of water molecules through
cerebral tissue in nuclear magnetic resonance
imaging and \citet{Libeskind13} introduced this concept in the context
of Cosmic Web classification schemes.

@@

%.........................................................................
%FIGURE 1: FA and vissual impression
\begin{figure*}
  \includegraphics[trim = 16mm 8mm 5mm 12mm, clip, keepaspectratio=true,
  width=0.73\textheight]{cosmicweb_FA_Tweb.pdf}
  \includegraphics[trim = 16mm 8mm 5mm 12mm, clip, keepaspectratio=true,
  width=0.73\textheight]{cosmicweb_FA_Vweb.pdf}
  \caption{Visual impression of different fields in a slice of
    $1\hMpc$ width in the Bolshoi simulation.   
    Fractional Anisotropy field (left); cosmic web classification
    (middle) where voids are white, sheets are light gray, filaments
    are dark gray and knots are black; colored individual
    voids (right) found by the a watershed algorithm on the Fractional
    Anisotropy field. Top/bottom corresponds to the T-Web/V-Web.}
  \label{fig:FA_field}
\end{figure*}
%.........................................................................

@@

Usually, the threshold is a free parameter that is tuned to reproduce
the visual appearence of the comic web. 
In this paper we take a different approach.
In this work we propose an optimal value of the threshold based on the
maximization of the fractional anisotropy field in the locations label
as filaments and walls. 
This threshold does not enter into our computations. 
We simply offer this estimate as a guide to readers familiar with the
meaning of this threshold.

%-------------------------------------------------------------------------
%FIGURE 2: Distributions of FA and density regarding the Lambda_1 eigenvalue
\begin{figure*}
\centering

  \includegraphics[trim = 2mm 2mm 5mm 10mm, clip, keepaspectratio=true,
  width=0.35\textheight]{delta_L1.pdf}  
  \includegraphics[trim = 2mm 2mm 5mm 10mm, clip, keepaspectratio=true,
  width=0.35\textheight]{FA_L1.pdf}

  \captionof{figure}{\small Overdensity (left) and Fractional
    Anisotropy (right) with respect to the eigenvalue $\lambda_1$ 
    for each web scheme (T-Web, continous lines. V-Web, dashed lines) calculated 
    over all grid cells in the Bolshoi simulation. 
    Thick central lines are the median and filled regions include
    $50\%$ of the cells in each bin.
    This information is necesary to define void boundaries in
    the watershed algorithm. 
    The vertical lines show the equivalent threshold values for the
    T-Web and V-web in order to have voids composed by cells with
    Fractional Anisotrop equal or less than $0.95$. 
   This threshold on the eigenvalues does not influence our
   computations. 
   We show it as a guide to readers familiar with the
   order of magnitude expectation for this threshold.}
  \label{fig:L1_correlations}

@@

@@

The fractional anisotropy (FA), as developed by \citet{Basser95}, was 
conceived to quantify the anisotropy of the diffusivity of water
molecules through cerebral tissue in nuclear magnetic resonance imaging. 
Here we present the FA, much in the same way as \citet{Libeskind13},
to use it as a tracer of cosmic voids.

@@

In the left and middle panels of Fig. \ref{fig:FA_field} we show the
FA field and web classification for both  web schemes over a slice of
an N-body simulation (described in Section \ref{sec:simulations}). 
Comparing these two panels we see that voids and knots (white
and black in the middle panel of Fig. 1) display low FA values at
their  centres, becoming gradually more anisotropic at outer regions.  
On the other hand the filamentary structure (grey in the middle panel
of Fig. 1) is traced by high FA values.  
This characteristic is the  key to use the FA as a tracer of cosmic
voids.

@@

Voids are regions where $\lambda_3\leq\lambda_2\leq
\lambda_1\leq\lambda_{th}$. 
This implies that a void is completely fixed by the relative strength
of the $\lambda_1$ eigenvalue with respect to the threshold.   
As we increase/decrease the threshold value $\lambda_{th}$, voids
increase/decrease progressively through contours of
increasing/decreasing $\lambda_1$.  
Voids are thus characterized by low values of both FA and
$\lambda_1$.

In Fig. \ref{fig:L1_correlations} we show that the these two values
are indeed closely correlated.  
The right panel shows the correlation between $\lambda_1$ and $\delta$ for
all the grid cells in the simulation while the right panel shows the
correlation between $\lambda_1$ and the FA. This shows that the
overdensity has a large scatter at fixed $\lambda_1$.

From Figs. \ref{fig:FA_field} and \ref{fig:L1_correlations} we
conclude that the FA is a good tracer of voids as it is almost perfectly
correlated with low values of $\lambda_1$. 
We propose that voids should be composed completely by regions of
FA$<0.95$.
If we increase the values of $\lambda_1$ from its minimum until it
we reach FA$=0.95$ in \ref{fig:L1_correlations} we find that this
correspond to critical values of $\lambda_{1}^T = 0.265$ and
$\lambda_{1}^V = 0.175$ for the T-Web and V-Web, respectively.
This means that setting $\lambda_{th}$ to either
$\lambda_{1}^T$/$\lambda_{1}^{V}$ automatically produces voids with
all the cells FA$<0.95$.   
The middle panels in Fig. \ref{fig:FA_field} show the web
classification for this choice of $\lambda_{th}$, demonstrating that
this FA level is a sensitive choice to define voids.

@@

However, there are two main differences in our approach with respect to other
watershed implementations.
First, the watershed technique commonly uses the density field
instead of the FA field as we do here
\citep{Platen07,Neyrinck08}.   
Second, we estimate all relevant quantities on a Cartesian mesh of
fixed cell size, while other works use an adaptive Delaunay tessellation
\citep{Schaap00}.
However, from the analysis of our results the choice of a fixed
Cartesian mesh does not induce spurious results, at least with
the mass resolution we have in the N-body simulation.

The watershed algorithm also needs a threshold value to reduce
spurious features and prevent void hierarchization.  
If the density field is used, a typical threshold is
$\delta = -0.8$ \citep{Platen07},  which means that any ridge between
two voids with overdensity below that value is removed to merge the
respective voids. 
In our case we have to find a corresponding FA value
to define this threshold.

In Fig. \ref{fig:L1_correlations} we find the correlations of
the eigenvalue $\lambda_1$ with the matter overdensity (left panel) and
the FA (right panel).
We can use this information to find the equivalent FA threshold. 
From the left panel we see that an underdensity of $\delta=-0.8$ 
corresponds to $\lambda_1=0.0$, regardless of the web-finding
scheme.
From the second panel we have a very tight correlation of $\lambda_1$
with the FA, indicating that in turn $\lambda_1=0.0$ corresponds to a
FA=$0.65$ which is the value that we choose to remove ridges. 
The right column in Fig. \ref{fig:FA_field} shows all the individual
voids that have been identified using the watershed algorithm on the
FA field.

%.........................................................................
%FIGURE 3: volume functions
\begin{figure*}
\centering

@@

  \captionof{figure}{\small Left panel, void size distribution. Right
    panel, fraction of overcompensated/subcompensated ($C>1/C<1$)voids as a
    function of the effective radius. The continous (dashed)
    curves correspond to the T-Web (V-Web).
    The abundance for small ($r_{eff}<2.0\hMpc$) overcompensated voids
    shoots up in the V-Web scheme.
    We provide in the body of the paper two reasons for this behaviour.}
  \label{fig:volume_function}

@@

We limit our results to voids with effective radius larger than the
smoothing length of the density field, i.e. $\sim 1$\hMpc.  
Below that scale numerical resolution effects become important. 
With that choice we find a void volume filling fraction $54.88\%$ and
$47.06\%$ for the FA-Vweb and the FA-Tweb, respectively.

@@

Comparing the abundance of large voids in the two web schemes, we find
that the largest voids in the V-Web have $r_{\rm eff}\sim 10$\hMpc,
while the T-Web scheme includes voids as large as $r_{\rm eff}\sim 15$\hMpc. 
This suggests that large voids in the T-Web scheme have a velocity
structure that splits them in the V-Web. 
This increased granularity in the velocity structure of voids is
evident in the left and right panels of Fig. \ref{fig:FA_field}.

%.........................................................................
%FIGURE 4: Density profile of voids for each defined scheme
\begin{figure*}
\centering
  \includegraphics[trim = 2mm 2mm 5mm 0mm, clip, keepaspectratio=true,
  width=0.35\textheight]{voids_density_TwebFAG0.pdf}
  \includegraphics[trim = 2mm 2mm 5mm 0mm, clip, keepaspectratio=true,
  width=0.35\textheight]{voids_density_TwebFAG1.pdf}

@@

We find that voids are distributed in two different families
differentiated by the 
presence/absence of an overdense matter ridge in their density
profiles. 
To discriminate each void in one of the families we use the
compensation  index $\mathcal{C}$.
It is defined as the mass of a void enclosed in a spherical volume of
radius $R$ and normalized by the mass of the same volume assuming
it is filled by matter with the mean background density.

\eq{compensation}
{\mathcal{C} = \frac{M_v}{\overline{M}} = \frac{3}{2R^{3}} \int_0^{R} [\delta(r) + 1] r^2 dr}

We choose an integration radius of $R=4\reff$, that is large enough to 
enclose the compensation ridge for a typical void in case there is one. 
This leads us to voids with $\mathcal{C}>1$ having more mass than expected, 
constituting the family of overcompensated voids. 
These voids generally  exhibit a compensation ridge associated to
dense nearby structures. 
In the same fashion, voids with $\mathcal{C}<1$ constitute the family
of  subcompensated voids.

In Fig. \ref{fig:density_profile} we show the density and velocity profiles
of voids splitted in these two families. 
In the left column it becomes clear the difference between sub- and
overcompensated voids.

%.........................................................................
\begin{table}[!htbp]
\centering
\begin{tabular}{c | c c | c c}
\toprule
\multicolumn{1}{c}{}&  \multicolumn{2}{c}{\textbf{Tweb}} & \multicolumn{2}{c}{\textbf{Vweb}}\\
%\midrule
\textbf{${\bf r_{\rm eff}}$[\hMpc]}   & $\bf{C<1}$   & $\bf{C>1}$    & $\bf{C<1}$   & $\bf{C>1}$\\ \hline
%\midrule
$<2.0$        &  997 & 495   & 13480  & 711\\
$2.0-3.2$     &  791 & 471   & 2581   & 583\\
$3.2-4.4$     &  941 & 469   & 2168   & 656\\
$4.4-5.6$     &  869 & 467   & 1934   & 724\\
$5.6-6.8$     &  769 & 395   & 1287   & 584\\
$6.8-8.3$     &  665 & 362   & 700    & 315\\
$8.3-12.0$    &  587 & 333   & 123    & 61\\
$>12.0$       &  29  & 23    & 0      & 0\\ \hline
\textbf{total}& 5648 & 3015  & 22273  & 3634\\
\bottomrule
\end{tabular}
\caption{Number of voids for each bin of effective radius and for 
subcompensanted and overcompansated samples.}
\label{tab:number_voids}
\end{table}
%.........................................................................

Table \ref{tab:number_voids} lists the number of voids in 
each effective radius bin for the two web finding methods.

@@

The first interesting result is the overdensity value at the void's
center.
We find that larger voids have a lower overdensity value.
The largest voids ($8.3-12\ \hMpc$) have an underdensity
$\sim-0.95$ while smaller voids  ($2-3.2\ \hMpc$) fall around $\delta\sim 
-0.8$ at their centers.
This holds for both web schemes. 
These values are consistent with most of the void finding schemes
based on smooth and continuous fields from simulation or
reconstruction procedures on surveys \citep{Plionis02, Colberg05,
  Shandarin06,  Platen07, Neyrinck08, MunozCuartas11, Ceccarelli13,
  Paz13, Neyrinck13, Ricciardelli2013}, unlike geometrical approaches based 
on point distributions, where central density values are generally higher
\citep{Colberg08}.

A second feature about these profiles is their steepnes at inner
regions.  
In subcompensated voids, larger voids are steeper.
Smaller voids exhibit moderate slopes, reaching the mean density at
larger radii than larger voids.
This suggests that smaller subcompensated voids are embedded into low
density structures, while large subcompensated voids are surrounded
by dense structures, reaching the mean density at lower effective
radii than smaller voids. 
In the overcompensated case larger voids reach first  both the
compensation ridge and then the mean density value.

@@

All the previous results hold for both finding schemes.
This suggests an universal behaviour for the radial density profile in
two families of subcompensated and overcompensanted voids. 
This goes in the same direction of recent results about the internal
\citep{Colberg05,  Ricciardelli2013} and external structure of voids
\citep{Lavaux12, Ceccarelli13, Paz13, Hamaus14}. 
Our results extend the findings of \cite{Hamaus14} into the range of
voids with size $r_{\rm eff}<10$\hMpc.

@@

We find that subcompensated voids have outflowing velocity profiles
all the way up to the effective radius where the average radial
density reaches the average value.
For voids with sizes $r_{\rm eff}<8\hMpc$ the outflow is always
positive, consistent with the fact that their density profiles do not
reach the level $\delta=0$ in the range of explored radii.
This behaviour indicates that matter is being pulled out of the void
into external higher density features.

@@

Fig. \ref{fig:FA_profile} shows the results for the FA profiles.
We find that the FA clearly magnifies the difference between the
internal profile $r_{\rm eff}<1$ and the external profile $r_{\rm
  eff}>1$. 
Subcompensanted voids in the T-Web reach an asymptotic background
value of F=$0.8$ almost right at $r_{\rm eff}=2$. 
For the V-Web the results are similar, albeit rather slowly with the
effective radius.
Overcompensated voids reach a maximum FA at the same effective radiuus
$r_{\rm eff}=1$ and decline to reach an asymptotic value of FA=$0.85$
at larger radii.

@@

The difference between the radius where the density ridge is reached 
($r_{\rm eff}=3$) and the radius of the FA  ridge ($r_{\rm eff}=1$ )
justifies in a more quantiative way the qualitative argument
we present in sub-section \ref{subsec:watershed} to define void boundaries in
our method.  
Namely that as we increase the void boundary, we reach
first middle density walls, before reaching high density structures
associated with high anisotropy. 
This makes the FA ridge a reasonable
boundary for voids compared to the traditional definition that puts
the boundary at the density ridge.

@@

A second step in the void characterization 
is the separation into subcompensated and overcompensated samples. 
In the T-Web $35\%$ of the voids are overcompensated ($65\%$
subcompensated), meaning that they are located in denser regions with
a clear delimiting ridge.   
For the V-web the subcompensated fraction rises from $65\%$ to $85\%$ as the
void size decreases, supporting the picture of smaller spurious voids
located in medium density matter sheets.

Finally we proceed with an more detailed void characterization
through the radially averaged profiles of density, radial velocity and
fractional anisotropy. 
In this case we study separately the subcompensated and
overcompensated voids, split this time in samples with different
effective radii.

For the density the most interesting feature is that the  profile has
a similar shape for all the different void sizes once the radial
coordinate is expressed in units of the effective radius.  
In these profiles it is evident the presence of an overdense ridge
around $2<r/r_{\rm eff}<3$ for the overcompensated voids.
Subcompensated voids do not show such a ridge keeping its density
lower than the average value up to $r/r_{\rm eff}\sim 8$.
